The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-28 paper.tex
update

  On the basis of this setup, we cover the AMR base level with\
  $16\times16\times32$ root cells, refined progressively on the mid-plane $z=0$\
  based on the gradient of mass density.\
  We also restrict the refinement level is 7 within the cold disk so that\
  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.

@@

\subsection{Jet injection}
  The core of this work is to release the caveat that the jet direction must be perpendicular to the Galactic plane.\
  We resolve the jet source at the center of the simulation domain,\
  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\

@@

\subsection{X-ray and Gamma-ray emission}

@@

Inverse Compton scattering
\begin{equation}
  \frac{dE}{dtd\epsilon_{1}dV} = \frac{3}{4}\sigma_{T}c\textit{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
               \frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{max}}}_{\gamma_{\text{min}}\left(\epsilon\right)}
               \gamma^{-(p+2)}f(q, \Gamma)d\gamma.
\end{equation}

@@

Hadronic process
\begin{equation}
  \frac{dE}{dtd\epsilon_{1}dV} = cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
\end{equation}

>>>>

  On the basis of this setup, we cover the AMR base level with\
  $16\times16\times32$ root cells, refined progressively on the mid-plane $z=0$\
  based on the gradient of mass density.\
  We also restrict the refinement level at 7 within the cold disk so that\
  a molecular cloud can be adequately resolved by approximately 30 cells along their diameter, 20 pc.

@@

\subsection{Inclined jet injection}
  Recent paper \citep{Gallimore2006} has proposed that\
  there is a lack of preferred orientation of jets with respect to the plane of the disc.\
  There are a number of galaxies in which the jets are inclined to the disc normal\
  (e.g. NGC 3079, \citealt{Cecil2001}; NGC 1052, \citealt{Dopita2015}),\
  including galaxies in which the jets lie in the plane of the disc (e.g. IC 5063, \citealt{Morganti2015}).

  Motivated by these observations, we simulate three different inclined angles
  $10^{\circ}$, $45^{\circ}$, and $80^{\circ}$ with respect to the Galactic plane to\
  release the caveat that\
  the jet direction must be perpendicular to the Galactic plane, and in particular to\
  investigate the effect of inclined angle on the shape of bubbles.

  The jet is constantly ejected from a cylindrical source with
  four-velocity

  the density contrast between the thermal gas contained in the jets
  and the ambient gas

  We resolve the jet source at the center of the simulation domain,\
  cells are refined to level 11, leading to a finest spatial resolution of 0.4 pc.\

@@

\section{Results}

\subsection{X-ray emission}

@@

\subsection{Gamma-ray emission}

\subsubsection{Leptonic process}

\begin{equation}
  \frac{dE}{dtd\epsilon_{1}dV} = \frac{3}{4}\sigma_{T}c\textit{C}\epsilon_{1}\int^{\epsilon_{\text{max}}}_{\epsilon_{\text{min}}}
               \frac{n(\epsilon)}{\epsilon}d\epsilon\int^{\gamma_{\text{max}}}_{\gamma_{\text{min}}\left(\epsilon\right)}
               \gamma^{-(p+2)}f(q, \Gamma)d\gamma.
\end{equation}

@@

\subsubsection{Hadronic process}

\begin{equation}
  \frac{dE}{dtd\epsilon_{1}dV} = cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
\end{equation}
